\cleardoublepage
\thispagestyle{empty}
\section*{Aknowledgements}
I would like to thank Prof. Dr. Lukas Novotny, Dominik Windey and Dr. Ren\'{e} Reimann for the opportunity of working on this semester thesis.

During the entire project I could always rely on the supervision of either Dominik Windey or Dr. Ren\'{e} Reimann if questions of any sort arose. Their knowledge and the time they took to explain the principles of cavity dynamics in the context of this thesis was very much appreciated. Furthermore, I like to thank them for reading this report and being upfront and honest with their criticism, which helped to greatly improve the quality of this work.

Many thanks go to Anna Kuzmina. Her help was not only appreciated but also crucial to many insights that were gained during the course of this work. The many hours which she spent assisting my project were invaluable. She was always patient and precise while helping me and offered a lot of new ideas during the many discussions we had.

Furthermore, I also want to say a special "thank you" to Dr. Martin Frimmer for the many instances where he made suggestions and the many times he gave valuable tips regarding this work.

Additionally, I want to thank Dr. Achint Jain, who assisted me greatly with the AFM measurements and the evaluation of the data, even though he also had to prepare his PhD defense.

Finally, I want to thank every member of the Photonics Laboratory, for all the interesting discussions, the help and the generally friendly, open and inclusive environment I had the privilege to work in.